---
title: "database_interaction_functions"
author: "Tim Mooney"
date: "2024-05-15"
output: html_document
---

# Overview
The purpose of this document was to first explore how bits of the SQLite X R integration packages work and then to attempt functionising any code so that they can later be used in parts oft he workflow and server of the app, writing and querying files to/from a database.

Steps:
- Create and connect to a dummy database locally
- Load some dummy data from elsewhere
- Write the dummy data to the dummy database and fucntionise code
- Query the data back into the session and functionise that process too

load libraries
```{r}
library(tidyverse)
library(DBI)
library(RSQLite)
```
# Set directory to work locally
```{r}
# set durectory to work locally first, found this easier
setwd("~/Documents/hackafun/")
```

# Create a Database
```{r}
database = DBI::dbConnect(RSQLITE::SQLite(), dbname="~/Documents/hackafun/demoApp_db.sqlite")
```

# Load some Data
```{r}
df_automotive <- read_csv("dummy_data_schema_tm/data/dummy_data_automotive.csv")
```

# Connect to SQLite Database
```{r}
# connect to the database
database <- DBI::dbConnect(RSQLite::SQLite(), "demoApp_db.sqlite")
```

# Write Files to Database
#### First, Simply Write a File to DB
```{r}
dbWriteTable(conn = database, name = "automotive_df", df_automotive, overwrite = TRUE, append = FALSE)
```
#### Write Function for Adding Files
```{r}
demoapp_writetoDB <- function(data,
                              name = "",
                              database_dir = "",
                              overwrite = TRUE,
                              append = FALSE) {
    # connect to the database
  database <- DBI::dbConnect(RSQLite::SQLite(), database_dir)
  
   # write the data table to the database
  DBI::dbWriteTable(value = data, name = , name, conn = database, overwrite = overwrite, append = append)
  
   # disconnect from the database
  DBI::dbDisconnect(database)
}

# now try testing the above function
demoapp_writetoDB(data = df_automotive,
                  name = "automotive_df",
                  database_dir = "~/Documents/hackafun/demoApp_db.sqlite",
                  overwrite = TRUE,
                  append = FALSE)
```

# List Files in the Database
```{r}
# dbListTables(database) # list tables in database
# dbListFields(database, "automotive_df") # lists columns in table
```

# Retrieve Files from Database
#### First, Simply Query some Columns from DB
```{r}
automotive_df_queried <- dbGetQuery(conn = database, "SELECT date, text, sentiment FROM automotive_df")
```
#### Function for Retreiving Files
```{r}
demoapp_queryDB <- function(selected_table = "",
                            database_dir = "",
                            columns) {
  # connect to the database
  database <- DBI::dbConnect(RSQLite::SQLite(), database_dir)
  
  # if-else statement to define the select statement and query
  if (missing(columns) || "all" %in% columns) {
    select_statement <- paste("SELECT * FROM", selected_table)
  } else {
    select_statement <- paste("SELECT", paste(columns, collapse = ", "), "FROM", selected_table)
  }
  
  # execute the query and retrieve data as selected
  result <- DBI::dbGetQuery(conn = database, statement = select_statement)
  
  # safely disconnect from the database
  DBI::dbDisconnect(database)
  
  return(result)
}

# now try testing the above function
trial_retrieval <- demoapp_queryDB(selected_table = "automotive_df",
                                   database_dir = "~/Documents/hackafun/demoApp_db.sqlite")
```
